Data tidying for peekbank analysis

### 2025-04-04 1_tidy_data.qmd
pipeline cleanup

---
title: "Data getter for peekbank analysis"
format: html
---

@@

```{r}
load(file = here("..", "peekbank-method", "cached_intermediates", "1_d_aoi.Rds"))
#cache this here as an interim hack until we bring in the full pipeline
saveRDS(d_aoi, here("cached_intermediates","1_d_aoi.Rds"))
```

@@

```{r}
load(here("..", "peekbank-method", "cached_intermediates", "1_cdi_subjects.Rds"))

>>>>

---
title: "Data tidying for peekbank analysis"
format: html
---

@@

```{r}
readRDS(file = here("cached_intermediates", "0_d_aoi.Rds"))
```

@@

```{r}
load(here("cached_intermediates", "0_cdi_subjects.Rds"))
